%-------------------------
% Data Science CV - Daffa Narendra Hutapea
% Formatted to follow the Hacktiv8 Shareable DS CV Template
% (Header with title + location, Summary, Education, Work Experience,
%  Skills by category, Projects with [Deploy] links)
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}

% Project heading: {title}{deploy-url}{date}
\newcommand{\resumeProjectHeading}[3]{
\vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} \enspace \href{#2}{\underline{[Deploy]}} & \textit{#3} \\
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Daffa Narendra Hutapea} \\ \vspace{3pt}
  {\large Data Scientist / Data Analyst} \\ \vspace{3pt}
  \small Jakarta, Indonesia $|$ +62 812 944 80320 $|$
  \href{mailto:narendra.daffa08@gmail.com}{narendra.daffa08@gmail.com} $|$
  \href{https://linkedin.com/in/daffa-hutapea}{\underline{LinkedIn}} $|$
  \href{https://github.com/daphutapea}{\underline{GitHub}}
\end{center}

%----------SUMMARY----------
\section*{Summary}
Mathematics graduate from Universitas Indonesia and a Hacktiv8 Full Time Data Science graduate, skilled in building and deploying machine learning and deep learning models (classification and computer vision) using Python and SQL. Combines a strong analytical and statistical foundation with proven leadership and organizational experience from large-scale university events. Eager to apply data-driven problem solving and a growth mindset to create business impact as a Graduate Trainee.

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Hacktiv8 Bootcamp}{April 2026 -- June 2026}
      {Full Time Data Science Program $|$ Current Score: 95\%}{Jakarta, Indonesia}
  \resumeSubheading
      {Universitas Indonesia}{July 2022 -- February 2026}
      {Bachelor of Science (B.Sc.) in Mathematics $|$ GPA: 3.45/4.00}{Depok, Indonesia}
  \resumeSubheading
      {SMA Negeri 99 Jakarta}{July 2019 -- May 2022}
      {Natural Science Major}{Jakarta, Indonesia}
\resumeSubHeadingListEnd

%----------WORK EXPERIENCE----------
\section{Work Experience}
\resumeSubHeadingList
  \resumeSubheading
      {PT Kimia Farma, Tbk}{July 2024 -- August 2024}
      {Big Data Analytics Intern}{Jakarta, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Gained hands-on experience in Data Warehouse process flow, Data Marts, Big Data concepts, and Data Pipeline management.}
          \resumeItem{\textbullet\ Wrote SQL queries (including Common Table Expressions) and performed Create, Select, Update, and Delete operations on a Database Management System.}
          \resumeItem{\textbullet\ Performed data analysis and visualization in Salesforce and built a sales dashboard in Google Looker Studio.}
          \resumeItem{\textbullet\ Delivered a final project analyzing Kimia Farma's business performance for 2020--2023.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

%----------SKILLS----------
\section{Skills \& Competencies}
\resumeSubHeadingList
  \resumeItem{\textbf{General Skills:} Exploratory Data Analysis, Machine Learning, Deep Learning, Computer Vision, Statistical Analysis, Data Visualization}
  \resumeItem{\textbf{Programming Languages:} Python, SQL, MATLAB/Octave, LaTeX}
  \resumeItem{\textbf{Libraries / Frameworks:} Scikit-Learn, TensorFlow, Keras, XGBoost, imbalanced-learn, Pandas, NumPy, Matplotlib, Seaborn}
  \resumeItem{\textbf{Modeling Algorithms:} Regression, Decision Trees, Random Forest, KNN, SVM, Boosting (XGBoost), Neural Networks (CNN)}
  \resumeItem{\textbf{Techniques:} Feature Engineering, Hyperparameter Tuning, Cross-Validation, Transfer Learning, Image Augmentation}
  \resumeItem{\textbf{Tools / Deployment:} Streamlit, Docker, Hugging Face Spaces, Git, Google Looker Studio, Microsoft Office, Google Workspace}
  \resumeItem{\textbf{Soft Skills:} Leadership, Teamwork, Problem Solving, Analytical Thinking, Communication}
  \resumeItem{\textbf{Languages:} Indonesian (Native), English (Professional Working Proficiency; TOEFL ITP Equivalent: 570)}
\resumeSubHeadingListEnd

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingList
  \resumeProjectHeading
      {Land-Use Classification of Satellite Imagery (Computer Vision)}{https://huggingface.co/spaces/dahutapea/Classification-of-Satellite-Imagery}{June 2026}
      \resumeSubHeadingList
          \resumeItem{Built a 5-class land-use classifier for Sentinel-2 satellite tiles (EuroSAT: AnnualCrop, Forest, Highway, Industrial, River) to enable large-scale land monitoring without manual photo-interpretation. Benchmarked a from-scratch CNN against a fine-tuned MobileNetV2 transfer-learning model trained on the same image-augmented data, reaching 97.1\% test accuracy, and deployed it as an interactive web app.}
          \resumeItem{\textbf{Technology / Tools:} Python, TensorFlow, Keras, MobileNetV2, Pandas, NumPy, Matplotlib, Seaborn, Streamlit, Docker, Hugging Face Spaces}
      \resumeSubHeadingListEnd
  \resumeProjectHeading
      {Auto-Insurance Claim Fraud Detection}{https://huggingface.co/spaces/dahutapea/insurance-fraud-detection}{May 2026}
      \resumeSubHeadingList
          \resumeItem{Developed a binary classification model as a claims-screening tool that assigns a fraud risk score to each auto-insurance claim, helping investigators prioritize which cases to review. Benchmarked five algorithms (Decision Tree, Random Forest, KNN, SVM, XGBoost) within an imbalanced-learn pipeline using SMOTE and 5-fold stratified cross-validation, then tuned the best model (XGBoost) with GridSearchCV and a recall-leaning decision threshold, and deployed it as an interactive web app.}
          \resumeItem{\textbf{Technology / Tools:} Python, Scikit-Learn, XGBoost, imbalanced-learn (SMOTE), Pandas, NumPy, Matplotlib, Seaborn, Streamlit, Docker, Hugging Face Spaces}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

%----------ORGANIZATIONAL EXPERIENCE----------
\section{Organizational Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Lecturer \& Laboratory Assistant -- Numerical Differential Equation}{February 2025 -- June 2025}
      {Universitas Indonesia}{Depok, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Taught and mentored 70+ second-year students per section in numerical programming using MATLAB and Octave.}
          \resumeItem{\textbullet\ Designed new teaching materials, timelines, and graded problem sets, and evaluated student performance.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Laboratory Assistant -- Numerical Methods}{February 2024 -- June 2024}
      {Universitas Indonesia}{Depok, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Instructed 50+ first-year students per section in Python and LaTeX and coordinated with 15+ fellow assistants.}
          \resumeItem{\textbullet\ Created teaching materials and problem sets and evaluated student assignments.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Lecturer Assistant -- Introduction to Data Science}{February 2024 -- June 2024}
      {Universitas Indonesia}{Depok, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Delivered supplementary lessons to 40+ students and evaluated their assignments to strengthen subject understanding.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {HIPMI PT UI 2023/2024}{September 2023 -- August 2024}
      {Staff of Creative Economy, MSMEs, and Startup Development}{Depok, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Served as Head of Event Runner at Makarapreneur, a national business plan competition.}
          \resumeItem{\textbullet\ Coordinated across the Visual Design, Public Relations, Operations, Logistics, and Competition divisions to deliver the Final Round and Gala Dinner.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Orientasi Kegiatan Kampus UI 2023 (OKK UI 2023)}{April 2023 -- August 2023}
      {Vice Head of Sponsorship}{Depok, Indonesia}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Approached 100+ corporations across Instagram, Email, and LinkedIn, securing sponsorship from 24+ companies (e.g. Gojek, Bank Indonesia, Frisian Flag, Telkomsel).}
          \resumeItem{\textbullet\ Led a team of sponsorship staff and coordinated with the treasurer to fulfill sponsor deliverables and accountability reports.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

%----------ACHIEVEMENTS----------
\section{Achievements}
\resumeSubHeadingList
  \resumeItem{\textbullet\ \textbf{Best Sponsorship Staff} -- OKK UI 2023; promoted to Vice Head of Sponsorship for outstanding performance.}
  \resumeItem{\textbullet\ \textbf{10th Highest Cumulative Score} -- 2022 Natural Science cohort, SMA Negeri 99 Jakarta.}
\resumeSubHeadingListEnd

%----------CERTIFICATIONS----------
\section{Certifications}
\resumeSubHeadingList
  \resumeSubheading
      {Lembaga Bahasa Internasional (LBI), Universitas Indonesia}{October 2022}
      {English Proficiency Test (EPT) -- Score: 570 (TOEFL ITP Equivalent), Grade: A}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Certificate No. 11959/UN2.F7.LBI/PDP.00.07.01/2022}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\end{document}
