\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Daffa Narendra Hutapea} \\
  \small +62 812 944 80320 $|$ \href{mailto:narendra.daffa08@gmail.com}{narendra.daffa08@gmail.com} $|$ 
  \href{linkedin.com/in/daffa-hutapea}{linkedin.com/in/daffa-hutapea} $|$ \href{https://github.com/daphutapea}{github.com/daphutapea} 
\end{center}

\section*{Summary}
A highly driven Mathematics graduate student at Universitas Indonesia with a strong interest in data science, analytics, and business development. Experienced in data analysis, data visualization, SQL querying, and database management through internship and academic experiences. Skilled in Python, SQL, Google Data Studio, and data modeling with numerous model predictions. Through various leadership and organizational experiences, consistently demonstrates strong analytical thinking, problem solving, and teamwork skills. Eager to further develop expertise and contribute in the field of data analytics and business-driven decision making.

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Hacktive8 Bootcamp}{April 2026 -- June 2026}
      {Hacktive8 Full Time Data Science Program $|$ Current Score: 95\%}{}
  \resumeSubheading
      {Universitas Indonesia}{July 2022 -- February 2026}
      {Bachelor Degree of Science (B.Sc.) in Mathematics $|$ Current GPA: 3.45/4.00}{}
  \resumeSubheading
      {SMAN 99 Jakarta}{July 2019 -- May 2022}
      {Natural Science Major}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ The $10^{th}$ Highest Cumulative Score of 2022 Natural Science Major Students}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Work Experiences}
\resumeSubHeadingList
  \resumeSubheading
      {PT. KIMIA FARMA, TBK}{July 2024 -- August 2024}
      {Big Data Analytics Intern}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Gained expertise in Data Warehouse process flow, the creation and importance of Data Marts, Big Data concepts, and Data Pipeline management.}
          \resumeItem{\textbullet\ Executed operations involving Common Table Expressions, basic SQL queries, and developed a deep understanding of Database Management Systems, including Create, Select, Update (Alter), and Delete (Drop) Table operations.}
          \resumeItem{\textbullet\ Engaged in Data Analysis and Data Visualization tasks within Salesforce and implemented it in the sales dashboard by Google Looker Studio.}
          \resumeItem{\textbullet\ Created a final project regarding the performance analysis of Kimia Farma Year 2020 - 2023.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Organizational Experiences}
\resumeSubHeadingList
  \resumeSubheading
      {Lecturer and Laboratory Assistant for Numerical Differential Equation}{February 2025 -- June 2025}
      {Universitas Indonesia}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Undertaking the responsibility of teaching and instructing second-year students in programming languages, with over 70 students in each section.}
          \resumeItem{\textbullet\ Teaching fundamental programming languages including MATLAB and Octave. Creating and updating a novel teaching course system for second-year students, which involves generating new teaching materials and timelines.}
          \resumeItem{\textbullet\ Creating problems that need to be solved by first-year students with the fundamental knowledge of MATLAB and Octave.}
          \resumeItem{\textbullet\ Evaluating the performance of the first-year students through assignments given by Lecturer and Laboratory Assistant.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Laboratory Assistant for Numerical Methods}{February 2024 -- June 2024}
      {Universitas Indonesia}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Undertaking the responsibility of instructing first-year students in programming languages, with over 50 students in each section.}
          \resumeItem{\textbullet\ Teaching fundamental programming languages including Python and LaTeX. Creating and updating a novel teaching course system for first-year students, which involves generating new teaching materials and timelines.}
          \resumeItem{\textbullet\ Collaborating and coordinating with over 15 laboratory assistants.}
          \resumeItem{\textbullet\ Creating problems that need to be solved by first-year students with the fundamental knowledge of Python and LaTeX.}
          \resumeItem{\textbullet\ Evaluating the performance of the first-year students through assignments given by Laboratory Assistants.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Lecturer Assistant for Introduction to Data Science}{February 2024 -- June 2024}
      {Universitas Indonesia}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Taking responsibility for teaching more than 40+ students as additional lessons regarding the mentioned course to increase their understanding on the subject.}
          \resumeItem{\textbullet\ Evaluating the performance of more than 40+ students through assignments given by Lecturers.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {HIPMI PT UI 2023/2024}{September 2023 -- August 2024}
      {Staff of Creative Economy, MSMEs, and Startup Development}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Head of Event Runner at Makarapreneur, a national business plan competition held by HIPMI PT UI and HIPMI Stocks.}
          \resumeItem{\textbullet\ Coordinated with the Visual Design division regarding the design of publication materials to be uploaded.}
          \resumeItem{\textbullet\ Coordinated with the Public Relations division regarding publication schedules and publication platforms.}
          \resumeItem{\textbullet\ Coordinated with the Operations and Logistics divisions regarding goods and consumption needs.}
          \resumeItem{\textbullet\ Coordinated with the Competition division regarding the organization of the Final Round \& Gala Dinner event.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Orientasi Kegiatan Kampus UI 2023 (OKK UI 2023)}{April 2023 -- August 2023}
      {Vice Head of Sponsorship}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Approached 100+ corporations to propose sponsorship from 3 social media platforms (Instagram, Email, LinkedIn) and marketing calls to offer sponsorship and partnership in the form of fresh money and in kind sponsorship.}
          \resumeItem{\textbullet\ Coordinated with OKK UI 2023's treasurer and successfully provided OKK UI 2023 with sponsorship and in kind sponsorship from 24+ corporations such as Gojek, Bank Indonesia, Frisian Flag, Serena, Telkomsel, etc.}
          \resumeItem{\textbullet\ Lead a group of other sponsorship staff as the vice-president of sponsorship team to held offline and online meetings with the Project Officer of OKK UI 2023 and 20+ corporations to propose sponsorship such as Mandiri, Bank BTN, PT KAI, Paragon Group (include Wardah, Emina, Kahf, and Tavi), etc.}
          \resumeItem{\textbullet\ Coordinated with all of the sponsorship team to create an accountability report of contra achievements documentations that the sponsors desired, such as sponsor logos on OKK UI 2023's banners, tenant provision for sponsors, etc.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingList
  \resumeSubheading
      {SMA Negeri 99 Jakarta}{July 2019 -- May 2022}
      {Highschool Diploma at Natural Science}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ The $10^{th}$ Highest Cumulative Score of 2022 Natural Science Major Students.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {OKK UI 2023}{April 2023 -- August 2023}
      {Vice Head of Sponsorship Team}{}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Awarded as Best Sponsorship Staff of OKK UI 2023 and hence got promoted to Vice Head of Sponsorship Team of OKK UI 2023.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Skills \& Competency}
\resumeSubHeadingList
  \resumeItem{\textbf{Language}: Proficient in Indonesian, Limited working proficiency in English}
  \resumeItem{\textbf{Technical}: Proficient in Microsoft Office (Word, Excel, PowerPoint), Google Suites (Drives, Slides, Spreadsheets, Google Data Studios), Python Programming}
  \resumeItem{\textbf{Others}: Leadership, teamwork, problem-solving, thorough calculation, analytical thinking}
\resumeSubHeadingListEnd

\end{document}